The B2B transfer system will be firstly tested for the transfer from SIS18 to ESR and further to CRYRING, So the existing transfer system from SIS18 to ESR and the application of the B2B transfer system from SIS18 to ESR to CRYRING will be introduced in this chapter. In Sec. 6.1, the existing transfer system is explained and the new application is introduced in Sec. 6.2.

Here three typical ESR operations are introduced. More detalis about the parameter of the B2B transfer from SIS18 to ESR and further to CRYRING, please see Appendix B.
\begin{itemize}
\item Operation 1: SIS18 h=1 transfer to ESR

The two bunches in SIS18 are compressed into one bunch, e.g. \SI{400}{\meV/\atomicmassunit} $H^{+}$. Then the bunch is injected into the injection orbit of ESR. After accumulating the beams from SIS18 e.g. by the barrier bucket, ESR moves the beams from the injection orbit to the designed orbit. The beam will be decelerated to \SI{30}{\meV/\atomicmassunit} and formated one bunch, which will be transferred to the only one bucket of CRYRING from the ESR injection orbit.

\item Operation 2: SIS18 h=4 transfer to ESR

There are four bunches in SIS18, e.g. \SI{30}{\meV/\atomicmassunit} $U^{28+}$. Only two continuous bunches out of four will be injected into the injection orbit of ESR. The other two bunches will be lost. The beam is accumulated in the injection orbit and decelerated to \SI{4}{\meV/\atomicmassunit}- \SI{10}{\meV/\atomicmassunit} in the design orbit. Then $U^{89+}$ beam is transferred to CRYRING in the injection orbit, which is produced by $U^{28+}$ going through the stripper in the beam transfer line.
\item Operation 3: Transfer from SIS18 to ESR via FRS

The heavy ion beam in SIS18 is always compressed to one bunch and extracted from SIS18 and transferred to a target, e.g. fragment separator (FRS). The rare isotope beam from the FRS facility is injected into ESR. The energy of the rare isotope beam after the target varies in a wide range. Here we use an applied case as an example, the energy before the FRS is \SI{550}{\meV/\atomicmassunit} and after is \SI{400}{\meV/\atomicmassunit}. The beam is accumulated in ESR e.g. by the barrier bucket.

\end{itemize}

\section{Existing transfer from SIS18 to ESR}

\section{B2B transfer from SIS18 to ESR to CRYRING}



