\documentclass[12pt,twoside]{report}

\usepackage{array, xcolor, lipsum, bibentry}
\usepackage[margin=3cm]{geometry}
\usepackage{sectsty}
\sectionfont{\huge}
\pagestyle{empty}
%\nopagenumbers
%\title{\bfseries\Huge Tom T. Texblog}
%\author{texblog+cv@gmail.com}
%\date{}
% 
\definecolor{lightgray}{gray}{0.8}
\newcolumntype{L}{>{\raggedleft}p{0.14\textwidth}}
\newcolumntype{R}{p{0.8\textwidth}}
\newcommand\VRule{\color{lightgray}\vrule width 0.5pt}
 

\begin{filecontents}{publication.bib}




@article{bai_bunch_2015,
	title = {{BUNCH} {TO} {BUCKET} {TRANSFER} {SYSTEM} {FOR} {FAIR}},
	url = {http://icalepcs.synchrotron.org.au/papers/wepgf119.pdf},
	urldate = {2016-09-23},
	journal = {In Proc. of ICALEPCS},
	author = {Bai, J. and Ferrand, T. and Beck, D. and Bär, R. and Kester, O. and Ondreka, D. and Prados, C. and Terpstra, W.},
	year = {2015},
	file = {[PDF] synchrotron.org.au:C\:\\Users\\Gilgil\\AppData\\Roaming\\Zotero\\Zotero\\Profiles\\y25mftub.default\\zotero\\storage\\G38R62RF\\Bai et al. - 2015 - BUNCH TO BUCKET TRANSFER SYSTEM FOR FAIR.pdf:application/pdf}
}

@article{ferrand_system_2014,
	title = {System {Simulation} of {Bunch}-to-{Bucket} {Transfer} {Between} {Synchrotrons}},
	url = {http://repository.gsi.de/record/184160/files/FG-GENERAL-28.pdf},
	urldate = {2016-09-23},
	journal = {GSI Scientific Report},
	author = {Ferrand, T. and Bai, J.},
	year = {2014},
	file = {[PDF] gsi.de:C\:\\Users\\Gilgil\\AppData\\Roaming\\Zotero\\Zotero\\Profiles\\y25mftub.default\\zotero\\storage\\8FJRG2F2\\Ferrand and Bai - System Simulation of Bunch-to-Bucket Transfer Betw.pdf:application/pdf}
}

@article{bai_first_2014,
	title = {{FIRST} {IDEA} {ON} {BUNCH} {TO} {BUCKET} {TRANSFER} {FOR} {FAIR}},
	url = {http://accelconf.web.cern.ch/AccelConf/PCaPAC2014/papers/fpo024.pdf},
	urldate = {2016-09-23},
	journal = {In Proc. of PCaPAC},
	author = {Bai, J. and Beck, D. and Bär, R. and Ondreka, D. and Ferrand, T. and Kreider, M. and Prados, C. and Rauch, S. and Terpstra, W. and Zweig, M.},
	year = {2014},
	file = {[PDF] cern.ch:C\:\\Users\\Gilgil\\AppData\\Roaming\\Zotero\\Zotero\\Profiles\\y25mftub.default\\zotero\\storage\\GTG7PPUU\\Bai et al. - FIRST IDEA ON BUNCH TO BUCKET TRANSFER FOR FAIR.pdf:application/pdf}
}

@article{jiao-ni_modified_2013,
	title = {Modified read-out system of the beam phase measurement system for {CSNS}},
	volume = {37},
	url = {http://iopscience.iop.org/article/10.1088/1674-1137/37/10/107004/meta},
	number = {10},
	urldate = {2016-09-23},
	journal = {Chinese physics C},
	author = {Jiao-Ni, Bai and Lei, Zeng and Biao, Wang and Peng, Li and Fang, Li and Tao-Guang, Xu and Zi-Gao, Li},
	year = {2013},
	pages = {107004},
	file = {Snapshot:C\:\\Users\\Gilgil\\AppData\\Roaming\\Zotero\\Zotero\\Profiles\\y25mftub.default\\zotero\\storage\\IEB9A7XZ\\meta.html:text/html}
}

@article{bai_development_2012,
	title = {The {Development} of {Timing} {Control} {System} for {RFQ}},
	url = {http://inspirehep.net/record/1364282?ln=de},
	abstract = {Timing control system based on VME configuration is developed to meet the need of 3.5 MeV RFQ. An EPICS driver is provided to control its work. The timing control system satisfies request after examination. In the future, it will be used in the machine running. This paper introduces the Timing control hardware, VME interface, EPICS driver for Timing control system and MEDM operator interface. Bai, Jiaoni; Xiao, Shuai; Xu, Taoguang; Zeng, Lei},
	urldate = {2016-09-23},
	journal = {In Proc. of LINAC},
	author = {Bai, Jiaoni and Xiao, Shuai and Xu, Taoguang and Zeng, Lei},
	year = {2012},
	file = {Full Text PDF:C\:\\Users\\Gilgil\\AppData\\Roaming\\Zotero\\Zotero\\Profiles\\y25mftub.default\\zotero\\storage\\QX45773N\\Bai et al. - 2013 - The Development of Timing Control System for RFQ.pdf:application/pdf;Snapshot:C\:\\Users\\Gilgil\\AppData\\Roaming\\Zotero\\Zotero\\Profiles\\y25mftub.default\\zotero\\storage\\GIPXJ9UC\\1364282.html:text/html}
}

@article{ferrand_system_2015,
	title = {{SYSTEM} {DESIGN} {FOR} {A} {DETERMINISTIC} {BUNCH}-{TO}-{BUCKET} {TRANSFER}},
	url = {http://accelconf.web.cern.ch/AccelConf/IPAC2015/papers/wepma024.pdf},
	urldate = {2016-09-23},
	journal = {In Proc. of IPAC},
	author = {Ferrand, T. and Bai, J.},
	year = {2015},
	file = {[PDF] cern.ch:C\:\\Users\\Gilgil\\AppData\\Roaming\\Zotero\\Zotero\\Profiles\\y25mftub.default\\zotero\\storage\\S9IEJPXC\\Ferrand and Bai - SYSTEM DESIGN FOR A DETERMINISTIC BUNCH-TO-BUCKET .pdf:application/pdf}
}

@article{kreider_launching_2014,
	title = {Launching the {FAIR} timing system with {CRYRING}},
	url = {http://accelconf.web.cern.ch/AccelConf/PCaPAC2014/papers/tco304.pdf},
	urldate = {2016-09-23},
	journal = {In Proc. of PCaPAC},
	author = {Kreider, M. and Bai, J. and Bär, R. and Beck, D. and Hahn, A. and Prados, C. and Rauch, S. and Terpstra, W. W. and Zweig, M.},
	year = {2014},
	file = {[PDF] cern.ch:C\:\\Users\\Gilgil\\AppData\\Roaming\\Zotero\\Zotero\\Profiles\\y25mftub.default\\zotero\\storage\\BFVZIJJD\\Kreider et al. - 2014 - Launching the FAIR timing system with CRYRING.pdf:application/pdf}
}

@article{beck_paving_2013,
	title = {Paving the {Way} for the {General} {Machine} {Timing} {System}},
	url = {https://www-acc.gsi.de/wiki/pub/Timing/TimingSystemDocuments/CSCOTG_SciRep2013.pdf},
	urldate = {2016-09-23},
	journal = {GSI Scientific Report},
	author = {Beck, D. and Adamczewski-Musch, J. and Bai, J. and Bär, R. and Frühauf, J. and Hoffmann, J. and Kreider, M. and Kurz, N. and Prados, C. and Rauch, S. and {others}},
	year = {2013},
	file = {[PDF] gsi.de:C\:\\Users\\Gilgil\\AppData\\Roaming\\Zotero\\Zotero\\Profiles\\y25mftub.default\\zotero\\storage\\UZMXUB34\\Beck et al. - Paving the Way for the General Machine Timing Syst.pdf:application/pdf}
}

@misc{kreider_receiver_????,
	title = {Receiver {Nodes} of the {General}  {Machine} {Timing} {System} for {FAIR} and {GSI}},
	url = {https://www-acc.gsi.de/wiki/pub/Timing/TimingSystemDocuments/GMT_TR_Description-v3.2.pdf},
	abstract = {This  document  summarizes  the  "Timing  Receivers",  which  are  part
  of  the  component General Machine Timing System” of the accelerator control system.},
	urldate = {2016-09-23},
	author = {Kreider, Mathias and Bai, Jiaoni and Beck, Dietrich and Prados, Cesar and Terpstra, Wesley and Rauch, Stefan and Zweig, Marcus},
	file = {GMT_TR_Description-v3.2 - GMT_TR_Description-v3.2.pdf:C\:\\Users\\Gilgil\\AppData\\Roaming\\Zotero\\Zotero\\Profiles\\y25mftub.default\\zotero\\storage\\6NCJ78U6\\GMT_TR_Description-v3.2.html:text/html}
}
\end{filecontents}
 
\begin{document}
 
\bibliographystyle{plain}
\nobibliography{publication}

\section*{Publications}
\hfill \break
\hfill \break
\begin{tabular}{L!{\VRule}R}

2015&\bibentry{bai_bunch_2015}\\[10pt]
	 &\bibentry{ferrand_system_2015}\\[10pt]

2014&\bibentry{bai_first_2014}\\[10pt]
	 &\bibentry{kreider_launching_2014}\\[10pt]
	 &\bibentry{ferrand_system_2014}\\[10pt]
2013&\bibentry{jiao-ni_modified_2013}\\[10pt]
	 &\bibentry{beck_paving_2013}\\[10pt]
	&\bibentry{kreider_receiver_????}\\[10pt]
2012	&\bibentry{bai_development_2012}\\[10pt]
	 
\end{tabular}

 
\end{document}